---
title: "CLT demonstration 09/12/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
input <- list()
input$distribution_type <- "binomial"
input$bi_prob <- .5

```

## Motivation + Basic description

This is project for Data Science Specialization taught by Coursera + John Hopkins University. Author decided to program Shiny application dealing with Central limit theorem.

It should help its users to build intuition around CLT concept through interaction. The application might be used in Stat 101 or equivalent courses.

Presentation contains adjusted version of actual code. If interested, you can find whole implementation in GitHub repository linked below.

[ShinyLink](https://github.com/fridrichmrtn/JHUDataScience/tree/master/DataProducts/wk4/CLT)  
[GitHubLink](https://github.com/fridrichmrtn/JHUDataScience/tree/master/DataProducts/wk4/CLT)


## Getting population distribution - code example

```{r, echo = TRUE, eval = FALSE}

    # getting bionomial population distribution example
    population_object <- list()
    
    if (input$distribution_type=="binomial"){
      
      p <- input$bi_prob

      population_object$pop_data <-  rbinom(10000, size = 1,
                              prob = input$bi_prob)
      
      population_object$pop_mju <- mean(population_object$pop_data)
      population_object$pop_sd <- sd(population_object$pop_data)
      population_object$density <- density(population_object$pop_data)
    } 
    
```

## Rendering population plot - code example (1/2)

```{r, echo = TRUE, eval = FALSE}
    
    # set margin
    par(mar= c(2.1,4.1,4.1,7.1))
    
    # create histogram
    h<-hist(population_object$pop_data,
         breaks = "Sturges",
         col = "#f5f5f5",
         border = "#e3e3e3",
         freq=T,
         main = "",
         xlab = "Population value")
    
    # plot mean
    abline(v = population_object$pop_mju, lwd = 2, lty = 2)

```

## Rendering population plot - code example (2/2)

```{r, echo = TRUE, eval = FALSE}
    
    # separate density
    density_est <- population_objectv$density
    
    # calculate and plot density line
    lines(density_est$x,density_est$y*diff(h$mids[1:2])*
            length(population_object$pop_data),
          col = "#3b7db5", lwd = 2, lty = 3)
    
    # plot legend
    legend("topright", 
      legend = c(expression(paste(mu," estimate")), "PDF"),
      col = c("black","#3b7db5"),
      lty = c(2,3),
      lwd = c(2,2),
      box.col = "white"    )

```

## Rendering population plot - result

```{r pressure, echo = F, eval = T}

    population_object <- list()
    
    if (input$distribution_type=="binomial"){
      
      p <- input$bi_prob

      population_object$pop_data <-  rbinom(10000, size = 1,
                              prob = input$bi_prob)
      
      population_object$pop_mju <- mean(population_object$pop_data)
      population_object$pop_sd <- sd(population_object$pop_data)
      population_object$density <- density(population_object$pop_data)
    } 
    
    par(mar= c(2.1,4.1,4.1,7.1))
    
    h<-hist(population_object$pop_data,
         breaks = "Sturges",
         col = "#f5f5f5",
         border = "#e3e3e3",
         freq=T,
         main = "",
         xlab = "Population value")
    
    abline(v = population_object$pop_mju, lwd = 2, lty = 2)
    
        density_est <- population_object$density
    
    lines(density_est$x,density_est$y*diff(h$mids[1:2])*
            length(population_object$pop_data),
          col = "#3b7db5", lwd = 2, lty = 3)
    
    legend(
      "topright", 
      legend = c(expression(paste(mu," estimate")), "PDF"),
      
      col = c("black","#3b7db5"),
      lty = c(2,3),
      lwd = c(2,2),
      box.col = "white"
    )

```

## Thank you for reviewing my work!